\documentclass[a4paper,10pt]{article}

% Packages
\usepackage[left=1.2cm, right=1.2cm, top=1.2cm, bottom=1.2cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

% Formatting
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]

% Document
\begin{document}

\begin{center}
    {\Huge \textbf{Janardhan Soni}}\\
    \vspace{4pt}
    MERN Stack Developer (Fresher)\\
    \vspace{6pt}
    Phone: +91-9981370009 \;|\;
    Email: janardhansoni355@gmail.com \;|\;
    GitHub: \href{https://github.com/Janardhan-soni}{github.com/Janardhan-soni} \;|\;
    LinkedIn: \href{https://www.linkedin.com/in/janardhan-soni-36287b264/}{linkedin.com/in/janardhan-soni}
\end{center}


\vspace{6pt}

\section{Career Objective}
Motivated and enthusiastic MERN Stack Developer fresher with strong knowledge of MongoDB, Express.js, React.js, and Node.js. Seeking an entry-level position to apply my skills in building scalable web applications while continuously learning and contributing to team success.

\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Frontend:} HTML5, CSS3, JavaScript (ES6+), React.js, Redux (Basics), Bootstrap, Tailwind CSS
    \item \textbf{Backend:} Node.js, Express.js, REST APIs
    \item \textbf{Database:} MongoDB, Mongoose
    \item \textbf{Tools:} Git, GitHub, Postman, VS Code, NPM
    \item \textbf{Other:} JWT Authentication (Basics), MVC Architecture, Debugging
\end{itemize}

\section{Projects}

\textbf{MERN Stack E-Commerce Website}\\
\textit{MongoDB, Express.js, React.js, Node.js}
\begin{itemize}[leftmargin=*]
    \item Developed a full-stack e-commerce web application with user authentication.
    \item Implemented product listing, cart functionality, and order management.
    \item Used JWT for secure login and MongoDB for data storage.
    \item Built responsive UI using React and Bootstrap.
\end{itemize}

\textbf{Task Management Application}\\
\textit{React.js, Node.js, Express.js, MongoDB}
\begin{itemize}[leftmargin=*]
    \item Created a task management system supporting CRUD operations.
    \item Designed user-friendly UI using React Hooks.
    \item Integrated REST APIs with MongoDB for persistent storage.
\end{itemize}

\textbf{User Authentication System}\\
\textit{Node.js, Express.js, MongoDB}
\begin{itemize}[leftmargin=*]
    \item Implemented secure user registration and login system.
    \item Used password hashing and JWT-based authentication.
    \item Validated inputs and handled errors efficiently.
\end{itemize}


\section{Education}

\textbf{Bachelor of Technology (Computer Science & Engineering)} \hfill 2025\\
Sage University, Indore\\
CGPA: 7.15

\vspace{4pt}

\textbf{Diploma in Computer Science & Engineering } \hfill 2022\\
Govt Polytechnic College, Ujjain \\
Percentage / CGPA: 6.29

\vspace{4pt}

\vspace{4pt}

\textbf{Secondary (10th)} \hfill 2016\\
MP Board\\
Percentage: 61%


\section{Internship / Training}
\textbf{MERN Stack Development Training} \hfill Duration\\
Institute / Platform Name
\begin{itemize}[leftmargin=*]
    \item Hands-on experience in developing full-stack web applications.
    \item Worked with REST APIs, databases, and frontend-backend integration.
\end{itemize}

\section{Certifications}
\begin{itemize}[leftmargin=*]
    \item MERN Stack Development Certification
    \item JavaScript / React Certification
\end{itemize}

\section{Strengths}
\begin{itemize}[leftmargin=*]
    \item Quick Learner
    \item Strong Problem-Solving Skills
    \item Team Player
    \item Good Communication Skills
\end{itemize}

\section{Personal Details}
\begin{itemize}[leftmargin=*]
    \item Languages Known: English, Hindi
    \item Location: Indore, [MP]
\end{itemize}

\end{document}
